---
title: 'Sim UI Experiments'
author: "TeamPSD"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output:
     word_document: default   
     html_document: default 
     
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = ".", output_format = "all") })     
     
---

To use the code in this Rmarkdown for each Team/Model in separate Rmarkdown, please do as follow:
  
- ensure that all library packages (as listed in the library chunk) are installed
   + uncomment the line pkgs (list of packages)
   + uncomment the line  install.packages(pkgs)
   + run the two lines in the console
   + comment out these lines before kniting the Rmd file
- change the working directory in RStudio to the location of the RMarkdown and include datafiles:
   + "mtl_menu.csv"
   + "ModelParameters.xlsx"
   + "mm_bc.xlsx", 
   + "mm_exp1.xlsx", and/or
   + "mm_exp2.xlsx", and/or 
   + "mm_exp3.xlsx" 
   + "teamsprepostMayEBPsy.xlsx"
- update the filter chuck to specify team and start date of MLT launch  

```{r filters, include=FALSE}
tm <- "MP" # Team Location
launch_date <-  "2015-11" # MTL launch date in the clinic, format must be "yyyy-mm"

## For initial location
## True pre-condition is April 2014- Mar 2015; however data doesn't exist until Nov 2014
## Mixed Precondition:  Nov 2014 - Oct 2015 
## Therefore, enter "2015-11" for first MTL location

```

```{r library, include=FALSE}
# pkgs <- c("readxl", "tidyverse", "huxtable","htmlTable")
# install.packages(pkgs)

library(tidyverse)
library(readxl)
library(huxtable)
library(htmlTable)

```



## MTL Menu
``` {r,echo=FALSE, fig.width=4, fig.height=4,fig.show='hold'}
#Read Data from MTL Menu
data=read.csv('mtl_menu.csv')

#Create vector of new column names using question title instead of variable descriptor
cols <- c("x",
          "y",
          "Schedule - How to manage team schedules 
          (i.e. clinics/grids) to meet patients needs.",
          "New patients - How to get new patients in care, 
          while meeting existing patients needs.",
          "Return to clinic - How return to clinic orders free 
          free us to get patients to the right treatment 
          at the right time.",
          "Overwork - How overbooking or overworking
          increases patient no shows.",
          "Psychotherapy - How to improve team psychotherapy 
          and patients' patterns of engagement.",
          "Evidence-based Psychotherapy - How to improve 
          evidence-based psychotherapy in our team.",
          "Evidence-based Pharmacotherapy - How to improve 
          evidence-based pharmacotherapy in our team.",
          "Referrals - How to manage referrals to our team and
          services (e.g. meds, therapy, group) within our team.",
          "Mix of services - How our patients engage in our 
          teams mix of services.",
          "Improvement - Which improvements will have the best 
          effects across our mix of services?",
          "Burnout - How to reduce provider burnout and improve 
          patient satisfaction with care.",
          "Staffing - How to improve team care with our 
          existing staff mix.",
          "Intake evaluations",
          "Care coordination",
          "Medication management",
          "Psychotherapy",
          "Groups",
          "Adjunctive services (i.e. art and recreation therapy, 
          peer support specialists)",
          "Depression",
          "PTSD",
          "Alcohol use disorder",
          "Opioid use disorder")
          
#Replace column names of original data set with new column name vector 
colnames(data) <- cols

#For loop for creating barplots of responses for questions with 5 point likert scale
for (x in 3:14){
par(cex.main=0.7)
barplot(table(factor(data[,x], levels = -2:2)),
        main=colnames(data)[x],
        names.arg = expression("Very High", "High", "Neutral", "Low", "Very Low"),
        cex.names=0.5,
        col="#003F72",
)
}

#For loop for creating barplots of responses for questions with 3 point likert scale
for (x in 15:24){
par(cex.main=0.7)
barplot(table(factor(data[,x], levels = -1:1)),
        main=colnames(data)[x],
        names.arg = expression("Yes", "Neutral", "No or doesn't apply"),
        cex.names=0.5,
        col="#003F72",
)
}
```


## Team Data Table - Medication Management Module


```{r mm_setup, include=FALSE}
mmpar <- read_excel("ModelParameters.xlsx", sheet = "MMParams", col_names = FALSE, range = "A1:F16")

mmpar.table1 <- mmpar[c(10, 15, 12, 5, 3, 1,7, 13, 14), c(1,3,2,4:6)] 
# Missing "Target Wait Time"

stu <- c( "(appt/wk)","", "(wks)", "(wks)", "(%)","(pts/wk)", "(wks)", "(%)", "(%)")

mmpar.table <- mmpar.table1 %>%
  mutate(X__5 = replace(X__5, X__1 == "Appointment Supply (75th percentile)", 
                        X__2[which(X__1 == "Appointment Supply (75th percentile)")]),
         X__2 = replace(X__2, X__1 == "Appointment Supply (75th percentile)", NA),
         X__3 = replace(X__3, X__1 == "Appointment Supply (75th percentile)", NA),
         X__4 = replace(X__4, X__1 == "Appointment Supply (75th percentile)", NA),
         X__5 = replace(X__5, X__1 == "Appointment Slots % (with X waiver)",
                        X__2[which(X__1 == "Appointment Slots % (with X waiver)")]),
         X__2 = replace(X__2, X__1 == "Appointment Slots % (with X waiver)", NA),
         X__1 = sub(" in MM", "", X__1),
         X__1 = replace(X__1, X__1 == "Median Engagement", "Engagement Duration (median)"),
         X__1 = replace(X__1, X__1 == "Starting Rate (mean)", "Start Rate (mean)"), 
         X__1 = paste0(X__1, stu)) %>%
  mutate_at(vars(2:5), funs(formatC(as.numeric(.),digits = 2, format = "f"))) %>%
  mutate_at(vars(2:5), funs(replace(., . == " NA", ""))) %>%
  add_row(X__3 = "AUD", X__2 = "DEP", X__4 = "OUD", X__5 = "OTHER", .before = 3)

```

#### MM Table without definition (similar to the UI)

```{r mm_table_NOdef, echo=FALSE}

htmlTable(mmpar.table[,-6], header = c(rep("",5)), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrrrr")

```

#### MM Table with definition

```{r mm_table_def, echo=FALSE}

htmlTable(mmpar.table, header = c(rep("",6)), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrrrrl")

```




## Sim UI Experiments - Medication Management Module

```{r dtfiles, include=FALSE}
#List of files in Working Directory
files <- list.files()
files <- files[grepl("\\.xls",files)]
files <- files[-grep("ModelParameters.xlsx|teamsprepostMayEBPsy.xlsx", files)]

# Read in files related to Experimental design
dgn_read <- function(x){
  dt <- read_excel(files[x], col_names = FALSE, range = "A12:B15")
  dt <- dt %>%
    mutate(file_name = files[x],
           Experiment = sub(".*_(.*)\\.xls.*", "\\1", file_name),
           Experiment = replace(Experiment, Experiment == "bc", "Base Case"),
           Experiment = replace(Experiment, Experiment == "exp1", "Experiment 1"),
           Experiment = replace(Experiment, Experiment == "exp2", "Experiment 2"),
           Experiment = replace(Experiment, Experiment == "exp3", "Experiment 3"),
           Model = sub("^(.*)_.*", "\\1", file_name),
           X__1 = sub("[[:punct:]]$", "", X__1)) %>%
    rename(`QHFD Process` = X__1) %>%
    select(-file_name)
  return(dt)
}

dgn_list <- lapply(1:length(files), dgn_read)
dgn <- do.call("rbind", dgn_list)

#Read in files related to graph paramenters
sim_read <- function(x){
  dt <- read_excel(files[x], col_names = TRUE, range = "A17:DA104")
  dt <- dt %>%
    mutate(file_name = files[x],
           Experiment = sub(".*_(.*)\\.xls.*", "\\1", file_name),
           Experiment = replace(Experiment, Experiment == "bc", "Base Case"),
           Experiment = replace(Experiment, Experiment == "exp1", "Experiment 1"),
           Experiment = replace(Experiment, Experiment == "exp2", "Experiment 2"),
           Experiment = replace(Experiment, Experiment == "exp3", "Experiment 3"),
           Model = sub("^(.*)_.*", "\\1", file_name))%>%
    select(-file_name) %>%
    gather(week, values, - c(Model, Experiment, `Model Variables`)) %>%
  mutate(week = gsub(".* (\\d+)$", "\\1", week),
         week = as.numeric(week)) %>%
  filter(!(`Model Variables` %in%  unique(dt$`Model Variables`[is.na(dt$`Week 1`)]))) %>%
  separate(`Model Variables`, c("Services", "Variables"), " - ") %>%
    select(Model, Experiment, everything())
}

sim_list <- lapply(1:length(files), sim_read)
sim <- do.call("rbind", sim_list)


bc <- read_excel(files[grep("bc", files)], col_names = FALSE, range = "A69:B104")


## VA Color Pallete
vacol <- c("#003F72", "#0083BE", "#C4262E", "#772432", "#598527", "#f3cf45","#f7955b","#839097",
             "#dcddde", "#cccc99", "#bec292")
```

```{r q_setup, include=FALSE}
rsh_ord <- c("Our Question", "Our Hypothesis", "Our Findings", "Our Decisions")
  
dgn <- dgn %>%
  spread(`QHFD Process`, X__2) %>%
  select( Experiment, rsh_ord)
  
```


```{r exp_setup, include=FALSE}

## Identify Changing variable

var_exp <- bc %>%
  rename(`Model Variables` = X__1, base_value = X__2) %>%
  filter(!is.na(base_value)) %>%
  mutate(Variable = `Model Variables`) %>%
  separate(`Model Variables`, c("Services", "Variables"), " - ") 

par_chng <- sim %>%
  filter(week == 1) %>%
  inner_join(var_exp, by = c("Services", "Variables")) %>%
  filter(Experiment != "Base Case") %>%
  mutate(chng = values - base_value) %>%
  filter(chng != 0) %>%
  select(Experiment, Services, Variables,Variable, values)


```


#### Team Experimental Design


```{r tab-word, echo=FALSE, warning=FALSE}
tt_ht <- hux(dgn, add_colnames = TRUE) %>%
  set_bold(1, 1:5,TRUE) %>%
  set_bottom_border(1:nrow(dgn), 1:5, TRUE) %>%
  set_wrap(TRUE)

tt_ht

```

#### Changes to Model Parameters Relative to Base Case

```{r mpar, echo=FALSE, warning=FALSE}
hux(par_chng) %>%
  select(Experiment, Variable, values) %>%
  add_colnames() %>%
  set_bold(1, 1:3,TRUE) %>%
  set_bottom_border(1, 1:3, TRUE) %>%
  set_col_width(c(0.3, 0.5, 0.2)) %>%
  set_number_format(,3,2) %>%
  map_align(by_cols("left", "left", "right"))
  

```


#### Team Graphs
#### Compare Patient Cohort: Booking Rate

```{r graphs, echo=FALSE}
sim %>%
  filter(Variables == "Booking Rate")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```

#### Compare Patient Cohort: Appointments in MM

```{r graphs2, echo=FALSE}
sim %>%
  filter(Variables == "Appointments in MM")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```

#### Compare Patient Cohort: Completing Rate

```{r graphs3, echo=FALSE}
sim %>%
  filter(Variables == "Completing Rate")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```

#### Compare Patient Cohort: Patients in MM

```{r graphs4, echo=FALSE}
sim %>%
  filter(Variables == "Patients in MM")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```

#### Compare Patient Cohort: Starting Rate

```{r graphs5, echo=FALSE}
sim %>%
  filter(Variables == "Starting Rate")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```

#### Compare Patient Cohort: Waiting to Start

```{r graphs6, echo=FALSE}
sim %>%
  filter(Variables == "Waiting to Start")  %>%
  ggplot(aes(x = week, y = values, group = Experiment, colour = Experiment)) +
  geom_line(aes(linetype = Experiment)) +
  scale_color_manual(values = vacol) +
  facet_wrap( ~ Services) +
  theme_bw() +
  theme(legend.position="top", legend.title=element_blank()) 

```


## P-Charts 

```{r all_setup, include=FALSE}

#Filter setup: refer to the filter chunk at the top of this file
ldt <- seq(as.Date(paste(launch_date, "01", sep = "-")), length = 13, by = "-1 months")
edt <- ldt[2] # end date of 1 year precondition
sdt <- ldt[13] # start date of 1 year precondition


dt <- read_excel("teamsprepostMayEBPsy.xlsx", sheet = "Sheet1")
dt_fmt <- dt %>%
  filter(team == tm) %>%
  mutate(templatecount = as.numeric(templatecount)) %>%
  mutate_at(vars(templatecount: diagvisitcount), funs(replace(., is.na(.), 0))) %>%
  mutate(pct = templatecount / diagvisitcount,
         Date = as.Date(paste(year, month, "01", sep = "-"))
  )%>%
  select(Date, team, pct) %>%
  filter(Date >= as.Date("2014-11-01"))


dt_yr1mn <- dt_fmt %>%
  filter((Date >= sdt) & (Date <= edt)) %>%
  mutate(avg_yr1 = mean(pct),
         ucl_yr1 = avg_yr1 + 3*sd(pct),
         lcl_yr1 = avg_yr1 - 3*sd(pct)) %>%
  select(-Date, -pct) %>%
  filter(row_number() == 1)

dt_lims <- dt_fmt %>%
  left_join(dt_yr1mn, by = "team") %>%
  gather(type, Percentage, -Date, -team) %>%
  mutate(type = replace(type, type == "avg_yr1", "average (first year)" ),
         type = replace(type, type == "ucl_yr1", "UCL (first year)"),
         type = replace(type, type == "lcl_yr1", "LCL (first year)"),
         type = replace(type, type == "pct", paste0(team[type == "pct"], " Data")),
         Percentage = round(Percentage * 100,0),
         vacol = "#0083BE",
         vacol = replace(vacol, type == "average (first year)", "#C4262E"),
         vacol = replace(vacol, type == "LCL (first year)", "#685BC7"),
         vacol = replace(vacol, type == "UCL (first year)", "#598527"))
         
dt_shd <- data.frame(team = unique(dt_lims$team),
                     xmin= sdt, 
                     xmax= edt, 
                     ymin=-Inf, ymax=Inf) 

vacol <- unique(dt_lims$vacol)
names(vacol) <- unique(dt_lims$type)

```

## Individual Location Data
#### Site


```{r mpd_graph, echo=FALSE }
dt_lims %>%
  ggplot(aes(x = Date, y = Percentage, group = type, colour = type)) +
  geom_line() + 
  scale_color_manual(values = vacol, limits = c("LCL (first year)", "average (first year)",
                                                "UCL (first year)")) +
  guides(colour = guide_legend(reverse=T)) +
  labs( y = "Evidence-based Psychotherapy (%)") +
  scale_x_date(date_labels = "%Y %b", date_minor_breaks = "1 month") +
  geom_rect(data = dt_shd, aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), 
            fill="grey", alpha=0.3, inherit.aes = FALSE) +
  theme_bw() +
  theme(legend.title=element_blank())
```