---
title: "Team Data Table"
author: "Savet Hong"
date: "March 22, 2018"
output: html_document
     
---

To use the code in this Rmarkdown for each Model in separate Rmarkdown, please do as follow:

- ensure that all library packages (as listed in the library chunk) are installed
- copy chuck containing R libraries 
- copy section of code for each model
    + setup for each model
    + table with and/or without definition
- include "ModelParameters.xlsx" in the same folder, if not then change file pathway to the data source    

```{r library, include=FALSE}

library(readxl)
library(dplyr)
library(tibble)
library(tidyr)
library(htmlTable)

```

## Care Coordination Model


```{r cc_setup, include=FALSE}
ccpar <- read_excel("ModelParameters.xlsx", sheet = "CCParams", col_names = FALSE)
ccpar.table <- ccpar[c(12,10,5,3,1,7),] # Select row and order to match UI
ccpar.table$X__2 <- formatC(ccpar.table$X__2, digits = 2, format = "f")

```

#### CC Table without definition (similar to the UI)

```{r cc_table_NOdef, echo=FALSE}

htmlTable(ccpar.table[,-3], header = c("",""), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lr")
```

#### CC Table with definition

```{r cc_table_def, echo=FALSE}
htmlTable(ccpar.table, header = c("","",""), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrl")
```

## Medication Management Model


```{r mm_setup, include=FALSE}
mmpar <- read_excel("ModelParameters.xlsx", sheet = "MMParams", col_names = FALSE, range = "A1:F16")

mmpar.table1 <- mmpar[c(10, 15, 12, 5, 3, 1, 13, 14), c(1,3,2,4:6)] 
              # Missing "Target Wait Time"

mmpar.table <- mmpar.table1 %>%
  mutate(X__5 = replace(X__5, X__1 == "Appointment Supply", 
                        X__2[which(X__1 == "Appointment Supply")]),
         X__2 = replace(X__2, X__1 == "Appointment Supply", NA),
         X__3 = replace(X__3, X__1 == "Appointment Supply", NA),
         X__4 = replace(X__4, X__1 == "Appointment Supply", NA),
         X__5 = replace(X__5, X__1 == "% Appointment Slots (has X-Waiver)",
                        X__2[which(X__1 == "% Appointment Slots (has X-Waiver)")]),
         X__2 = replace(X__2, X__1 == "% Appointment Slots (has X-Waiver)", NA)) %>%
  mutate_at(vars(2:5), funs(formatC(as.numeric(.),digits = 2, format = "f"))) %>%
  add_row(X__3 = "AUD", X__2 = "DEP", X__4 = "OUD", X__5 = "OTHER", .before = 3)

```

#### MM Table without definition (similar to the UI)

```{r mm_table_NOdef, echo=FALSE}

htmlTable(mmpar.table[,-6], header = c(rep("",5)), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrrrr")

```

#### MM Table with definition

```{r mm_table_def, echo=FALSE}

htmlTable(mmpar.table, header = c(rep("",6)), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrrrrl")

```


## Aggregate Model

```{r agg_setup, include=FALSE}
aggpar <- read_excel("ModelParameters.xlsx", sheet = "AggParams", col_names = FALSE, range = "A1:I12")

#Table data setup
aggpar.table.head <- aggpar[c(6,2),]
aggpar.table.body <- aggpar[c(2,1,5,3,4),] %>%
  mutate_at(vars(2:8), funs(formatC(as.numeric(.),digits = 2, format = "f"))) %>%
  rename(Intake = X__2, Psy = X__3, EBPsy = X__4, CC = X__5, MM = X__6, 
         Adjunctive = X__7, Group = X__8, Variable = X__1, Definition = X__9)

aggpar.table.body.shrt <- t(aggpar.table.body[,2:8]) 
colnames(aggpar.table.body.shrt) <- aggpar.table.body$Variable

aggpar.test <- as.data.frame(aggpar.table.body.shrt) %>%
  mutate(X__1 = row.names(.)) %>%
  select(X__1, everything()) %>%
  mutate_if(is.factor,funs(as.character)) %>%
  add_row(X__1 = as.character(aggpar[6,1]), `Appointment Supply` =
            as.character(aggpar[6,2]), 
          `True Missed Appointments %` = "Patients/Week",.before = 1) %>%
  add_row(`Appointment Supply` = "Appointment", `True Missed Appointments %` = 
           "True Missed",`Return Visit Interval` = "Return Visit", 
          `Median Engagement` = "Median", `Referral Percentage` = "Referral",
          .before = 2) %>%
  add_row(`Appointment Supply` = "Supply", `True Missed Appointments %` = 
           "Appointments %",`Return Visit Interval` = "Interval", 
          `Median Engagement` = "Engagement", `Referral Percentage` = "Percentage",
          .before = 3)

#Table definition
agg_def <- aggpar[c(6,2,1,5,3,4),c(1,9)]
```

#### Aggregate Table without definition (similar to the UI)

```{r agg_table, echo=FALSE}

htmlTable(aggpar.test, header = c(rep("",6)), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lrrrr")

```
#### Aggregate Table Definition

```{r agg_table_def, echo=FALSE}
htmlTable(agg_def, header = c("Concept", "Definition"), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data: Aggregate Table Concept Definition", align = "ll")

```

## Psy Model

```{r psy_datafiles, include=FALSE}
psypar1a <- read_excel("ModelParameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B35:D36")

psypar1b <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B40:D43")

flow <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B3:D7")

rvi <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B8:D12")

med <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B13:D14")

rvi_after <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B15:D23")

med_after <- read_excel("./original/modelparameters.xlsx", sheet = "PSYParams", col_names = FALSE, range = "B24:D32")
```

```{r psy_setup, include=FALSE}
# Team Data Table/Appointment Supply columns
ord1 <- c("Appt. Supply", "% AUD", "% DEP", "% OUD", "% PTSD")
psypar1 <- rbind.data.frame(psypar1a[1,], psypar1b) %>%
  mutate(X__1 = replace(X__1, X__1 == "PctPTSD", "% PTSD"),
         X__1 = replace(X__1, X__1 == "PctDep", "% DEP"),
         X__1 = replace(X__1, X__1 == "PctAUD", "% AUD"),
         X__1 = replace(X__1, X__1 == "PctOUD", "% OUD"),
         X__1 = replace(X__1, X__1 == "Baseline Appointment Supply", 
                        "Appt. Supply")) %>%
  mutate_if(is.numeric, funs(as.character)) %>%
  slice(match(ord1, X__1))

psypar1$X__2[which(psypar1$X__1 == "Appt. Supply")] <-  
                         paste0(psypar1$X__2[which(psypar1$X__1 == "Appt. Supply")], 
                                " Slots/Week")
#Patient Flow 
flow.order <- c("Starters who Initiate","Starters who Return Later", "Starters who Quit", "Initiators who Complete","Initiators who Return Later", "Initiators who Quit Early", "Completers who Graduate","Completers who Return")

## Need to calculate
## Starters who Quit
## Initiators who Return Later
## Completers who Return
flow1 <- flow %>%
  add_row(X__1 = "Starters who Quit") %>% 
  add_row(X__1 = "Initiators who Return Later") %>%
  add_row(X__1 = "Completers who Return") %>%
  mutate( X__2 = replace(X__2, X__1 == "Starters who Quit", 1 - 
            (X__2[which(X__1 == "Starters who Initiate")] + 
               X__2[which(X__1 == "Starters who Return Later")])),
          X__2 = replace(X__2, X__1 == "Initiators who Return Later", 1 - 
            (X__2[which(X__1 == "Initiators who Complete")] + 
               X__2[which(X__1 == "Initiators who Quit Early")])),
          X__2 = replace(X__2, X__1 == "Completers who Return", 1 - 
            (X__2[which(X__1 == "Completers who Graduate")]))) %>%
  slice(match(flow.order, X__1)) %>%
  mutate(X__2 = paste0(round(X__2, 2)*100, "%"))
          
# Return Visit Interval less than 3months
rvi1 <- c("N/A", "See table below", "N/A", 
          round(rvi$X__2[which(rvi$X__1 == "Frequency <3mo - 2-7Visits-n-More<3mo")],2) ,
          "See table below",
          round(rvi$X__2[which(rvi$X__1 == "Frequency <3mo - 2-7Visits-n-done")],2), 
          round(rvi$X__2[which(rvi$X__1 == "8plusfreq")],2),
          "See table below")

# Median Engagement Duration less than 3months
med1 <- c("Always 1 week", "See table below", "Always 1 week",
          round(med$X__2[which(med$X__1 == "Avg Time in Visit 2-7-n-Done")], 2),
          "See table below", 
          round(med$X__2[which(med$X__1 == "Avg Time in Visit 2-7-More<3mo")],2),
          "12weeks", "See table below")


# Return Visit Interval after than 3months
visit.order <- c("From 1 Visit", "From 2 to 7 Visits", "From 8 or More Visits")
rvi2 <- rvi_after %>%
  mutate(X__3 = sub(".*-(.*)$", "\\1", X__1),
         Visit = sub(".*-(.*Visit.*)-.*$","\\1", X__1)) %>%
  select(-X__1) %>%
  spread(X__3, X__2) %>%
  mutate(Visit = replace(Visit, Visit ==" 1Visit", "From 1 Visit"),
         Visit = replace(Visit, Visit =="12Visits", "From 2 to 7 Visits"),
         Visit = replace(Visit, Visit =="7Visits", "From 8 or More Visits")) %>%
  slice(match(visit.order, Visit)) %>%
  select(Visit, LowD, MidD, HighD) %>%
  rename(`First Quartile` = LowD, Mean = MidD, `4th Quartile` = HighD) %>%
  mutate_if(is.numeric, funs(round(.,2)))


# Median Engagement Duration after than 3months
med2 <- med_after %>%
  mutate(X__3 = sub(".* (.* Q.*)$", "\\1", X__1),
         Visit = sub("^(.*mo).*","\\1", X__1)) %>%
  select(-X__1) %>%
  spread(X__3, X__2) %>%
  mutate(Visit = replace(Visit, Visit =="From1-PL3mo", "From 1 Visit"),
         Visit = replace(Visit, Visit =="From2-7-PL3mo", "From 2 to 7 Visits"),
         Visit = replace(Visit, Visit =="From8PL-PL3mo", "From 8 or More Visits"))%>%
  slice(match(visit.order, Visit)) %>%
  mutate_if(is.numeric, funs(round(.,2)))

         
# Upper Table without Definition
psy1 <- psypar1[,-3] %>%
  rename(AppSupply = X__1, rate = X__2) %>%
  add_row(AppSupply = "", rate = "") %>%
  add_row(AppSupply = "", rate = "") %>%
  add_row(AppSupply = "", rate = "") %>%
  cbind(.,flow1[,-3], rvi1, med1)

# Lower Table without Definition
psy2 <- merge.data.frame(rvi2, med2, by = "Visit") %>%
  add_row(`First Quartile` = "First Quartile", Mean = "Mean", 
          `4th Quartile` = "4th Quartile", `Lower Q` = "First Quartile",
          `Mid Qs` = "Mean", `Upper Q` = "4th Quartile", .before = 1)

```

#### Psy Table without definition (similar to the UI)
```{r psy_table, echo=FALSE}
htmlTable(psy1, header = c(rep("",2), "Patient Flow", "", "Return Visit \nInterval (weeks)", "Median Engagement \nDuration"), rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", caption ="Team Data", align = "lllrcc")


htmlTable(psy2, header = c("", "Return Visit", "Interval after 3", "Months (weeks)",
                           "Engagement", "Time after 3", "Months (weeks)"),
          rnames = FALSE, css.cell = "padding-left: 1em; padding-right: 1em;", 
          #caption ="Team Data", 
          align = "lcccccc" )

```
