---
title: "Debugging code"
author: "Joyce Yang"
date: "November 15, 2018"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(error = TRUE, echo = TRUE)
```

```{r, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
setwd(("//vhapalmpncptsd1/Shared Research/TeamPSD/quant_workgroup/r"))

```

## Setting up the R environment and datasets
```{r}
library(readxl)
library(magrittr)
library(lubridate)
library(dplyr)
library(psych)
library(ggplot2)
```


```{r}
##set up both files as dataframes
comparator.df <- read.csv("comparatorsites_nov23_16.csv", header=TRUE) 
dropout.df <- read.csv(file="dropout.csv",header=TRUE) 
```

## In order to debug code for issues with merging, use TMH = 2089 as reference to check for frequency of appearance in each code chunk. In previous analyses, TMH = 2089 appeared surprisingly frequently. TMH is original name of the telemental health variable.

#Check for number of occurences of TMH = 2089 at each step
```{r}
sum(comparator.df$TMH == 2089)
```

```{r}
##set all variable names as lower case
names(comparator.df) <- tolower(names(comparator.df))

names(dropout.df) <- tolower(names(dropout.df))
```

#Check for number of occurences of tmh = 2089 at each step (now and into the future in lowercase)
```{r}
sum(comparator.df$tmh == 2089)
```


## Setup the CDW Comparator Data part 1

```{r numeric, include=TRUE}
##Set variables as numeric in order to manipulate later
#set up within original CDW dataframe 
##create combined variable in comparator.df based on the variable 'year' and the variable 'quarter'

comparator.df <- comparator.df %>%
  mutate_at(vars(totalencounters:x._cbt_sud_sessions), as.numeric) %>%
  mutate(year_q  = paste0(year, "-", quarter), 
         site_yq = paste0(sta6a,"-",year_q))

```

## Check for frequency of tmh = 2089 
```{r}
sum(comparator.df$tmh == 2089)
```

